hormones

### 2019-10-20 analysis/07_hormones.Rmd
new hormone and candidate gene plots

```{r characterization}
hormonecharplot <- function(myhormone, myylab){

@@

  hormones %>% 
    filter(study == "characterization",
           hormone %in% c(myhormone))  %>% 
  ggplot(aes(x = timepoint, y = plasma_conc, fill = timepoint, color = sex)) +
    geom_boxplot(aes(outlier.colour = timepoint), lwd=1.05) +
    theme(axis.text.x =  element_blank(),
          legend.position = "none") +
    scale_fill_manual(values = mycolors) +
    scale_color_manual(values = sexcolors) +
    labs(y = myylab, x = NULL) +
    guides(fill = guide_legend(order=1),
         color = guide_legend(order=2))
}

a <- hormonecharplot("prolactin", "PRL (ng/mL)")
b <- hormonecharplot("cort", "CORT (ng/mL)")
c <- hormonecharplot("progesterone", "PROG (ng/mL)") 
d1 <- hormonecharplot("estradiol", "E (ng/mL)")
d2 <- hormonecharplot("testosterone", "T (ng/mL)")
d <- plot_grid(d1,d2, nrow = 1)
abcd <- plot_grid(a, b ,c, d, labels = "AUTO")
mylegend <- get_legend(c + theme(legend.position = "bottom"))
plot_grid(abcd, mylegend, nrow = 2, rel_heights = c(0.85,0.15))

>>>>

```{r characterization, fig.width=5.5, fig.height= 3}
hormonecharplot <- function(myhormone, myylab){

@@

  hormones %>% 
    filter(study == "characterization",
           hormone %in% c(myhormone))  %>% 
    droplevels() %>% 
  ggplot(aes(x = as.numeric(timepoint), y = plasma_conc)) +
    geom_boxplot(aes(outlier.colour = timepoint, fill = timepoint, alpha = sex)) +
    theme_B3() +
    theme(axis.text.x =  element_blank(),
          legend.position = "none") +
    scale_fill_manual(values = mycolors) +
    scale_color_manual(values = sexcolors) +
    labs(y = myylab, x = NULL) +
    guides(fill = guide_legend(order=1),
         color = guide_legend(order=2)) +
    scale_alpha_manual(values = c(0.75,1)) +
    geom_smooth(aes(colour = sex)) +
    scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) 
  }

hormonecharplot("prolactin", "PRL (ng/mL)")

a <- hormonecharplot("prolactin", "PRL (ng/mL)")
b <- hormonecharplot("cort", "CORT (ng/mL)")
c <- hormonecharplot("progesterone", "PROG (ng/mL)") 
d1 <- hormonecharplot("estradiol", "E (ng/mL)")
d2 <- hormonecharplot("testosterone", "T (ng/mL)")
d <- plot_grid(d1,d2, nrow = 1)
abcd <- plot_grid(a, b ,c, d)
abcd
```
